---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

### Load the data
Load the data from the following [URL](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip) and read the data from it by "read.csv".
```{r loaddata, echo=TRUE}
filename1 <- "repdata_data_activity.zip"

#checking whether zip file exists or not.
if (!file.exists(filename1)){
  fileURL <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
  download.file(fileURL, filename1)
}  

filename2 <- "activity.csv"

#checking whether zip file is unzip or not
if (!file.exists(filename2)) { 
  unzip(filename2) 
}

#Read the original data  
data <- read.csv(filename2)
head(data)
```


### Process the original data
Using "dplyr" library, change the data format by "tbl_df".
```{r processdata, eho=TRUE}
library(dplyr)
data2 <- tbl_df(data)
head(data2)
```

## What is mean total number of steps taken per day?

1. Calculate the total number of steps taken per day.
```{r totalsteps}
data2_date <- group_by(data2, date)
df.total_steps <- summarise(data2_date, total_steps = sum(steps))
head(df.total_steps)
```

2. Make a histogram of the total number of steps taken per day.
```{r makehist}
with(df.total_steps,
         hist(df.total_steps$total_steps,
         xlab = "Total steps taken per day", 
         main = "Total steps taken per day"))
```

3. Calculate and report the mean and median of the total number of steps taken per day.
```{r meanandmedian}
mean.steps <- mean(df.total_steps$total_steps, na.rm = TRUE)
median.steps <- median(df.total_steps$total_steps, na.rm = TRUE)
paste("The mean of the total number of steps taken per day is", mean.steps)
paste("The median of the the total number of steps taken per day is", median.steps)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
