---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  word_document: default
---


## Loading and preprocessing the data

### Load the data
Load the data from the following [URL](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip) and read the data from it by "read.csv".
```{r loaddata, echo=TRUE}
filename1 <- "repdata_data_activity.zip"

#checking whether zip file exists or not.
if (!file.exists(filename1)){
  fileURL <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
  download.file(fileURL, filename1)
}  

filename2 <- "activity.csv"

#checking whether zip file is unzip or not
if (!file.exists(filename2)) { 
  unzip(filename2) 
}

#Read the original data  
data <- read.csv(filename2)
head(data)
```


### Process the original data
Using "dplyr" library, change the data format by "tbl_df". And it is named *data2*. Output is confirmed by "head" function.
```{r processdata, eho=TRUE}
library(dplyr)
data2 <- tbl_df(data)
head(data2)
```

## What is mean total number of steps taken per day?

1. Calculate the total number of steps taken per day.

*data2* is grouped by *date*. And the summation of *steps* per day is calculated and saved into *df.total_steps*. Output is confirmed by "head" function. 

```{r totalsteps, eho=TRUE}
data2_date <- group_by(data2, date)
df.total_steps <- summarise(data2_date, total_steps = sum(steps))
#summarize(data2_date, mean.steps = mean(steps, na.rm = TRUE))
head(df.total_steps)
```

2. Make a histogram of the total number of steps taken per day.

Using *df.total_steps*, histogram is made.
```{r makehist, echo=TRUE}
with(df.total_steps,
         hist(df.total_steps$total_steps,
         xlab = "Total steps taken per day", 
         main = "Total steps taken per day"))

# Save png file
dev.copy(png, file = "histogram.png")
dev.off()

```

3. Calculate and report the mean and median of the total number of steps taken per day.

The mean and median of the steps taken per day is calculated with *df.total_steps*. And the results are pasted. During this calculation, NA data is removed.
```{r meanandmedian, eho=TRUE}
mean.steps <- mean(df.total_steps$total_steps, na.rm = TRUE)
median.steps <- median(df.total_steps$total_steps, na.rm = TRUE)
paste("The mean of the total number of steps taken per day is", mean.steps)
paste("The median of the the total number of steps taken per day is", median.steps)
```

## What is the average daily activity pattern?
Make a time series plot of the 5-minute interval (x-axis) for each date.
```{r interval, eho=TRUE}
library(ggplot2)
ggplot(data2, aes(x = interval, y = steps, color = date)) +
  geom_line()

dev.copy(png, file = "interval.png")
dev.off()

```

the average number of steps taken, averaged across all days (y-axis).  

```{r avealldays, eho=TRUE}
data2_interval <- group_by(data2, interval)
df.ave_steps <- summarise(data2_interval, averaged_steps = mean(steps, na.rm = TRUE))
head(df.ave_steps)
```


To find which 5-minute interval contains maximum number of steps, data is arranged by the averaged_steps. Then, the interval which appears in the first row is what this question is requesting. 

```{r maxinterval, eho=TRUE}
df <- arrange(df.ave_steps, desc(averaged_steps))
paste("5-minute interval which contains the maximum number of steps across all the days in the dataset is",
      as.numeric(df[1, 1]))
```

## Imputing missing values
Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r countNA, eho=TRUE}
paste("The total number of rows with NAs is", sum(is.na(data2$steps)))
 
```
Strategy for filling in all missing values in the dataset is to use the mean for all day.

Create a new dataset that is equal to the original dataset but with the missing data filled in as *data2_filled*.
And missing value was replaced by 37 (same value as mean step through all day)
```{r filled, echo=TRUE}
data2_filled <- data2
#mutate(data2, steps = recode(steps, NA = )
#a <- mean(data2$steps, na.rm = TRUE)
data2_filled[is.na(data2$steps), 1] <- 37
# mean(data2$steps, na.rm = TRUE)
#<- data2[is.na(data2$steps), mean(data2$steps, na.rm = TRUE)]
```

Make a histogram with *data2_filled* and calculate mean and median total numner of steps.
```{r makehist2, echo=TRUE}
data2_filled_date <- group_by(data2_filled, date)
df2.total_steps <- summarise(data2_filled_date, total_steps = sum(steps))

with(df2.total_steps,
         hist(total_steps,
         xlab = "Total steps taken per day", 
         main = "Total steps taken per day"))

# Save png file
dev.copy(png, file = "histogram2.png")
dev.off()

mean.steps2 <- mean(df2.total_steps$total_steps, na.rm = TRUE)
median.steps2 <- median(df2.total_steps$total_steps, na.rm = TRUE)
paste("The mean of the total number of steps taken per day after filled in is", mean.steps2)
paste("The median of the the total number of steps taken per day after filled in is", median.steps2)

```
Mean value is 1.002 times larger than the the first part of the assignment.
Median value  is 1.02 times larger than the the first part of the assignment.

## Are there differences in activity patterns between weekdays and weekends?
Create *category2* variable which shows each date is weekday or weekend using wday function.
```{r week, echo=TRUE}
library(lubridate)
date_POSIX <- as.POSIXct(strptime(data2_filled$date, "%Y-%m-%d"))
data3 <- mutate(data2_filled, date_POSIX = date_POSIX)
data3 <- mutate(data3, category = wday(date_POSIX))
data3 <- mutate(data3, category2 = case_when(
  category == 1 ~ "weekend",
  category == 7 ~ "weekend", 
  TRUE ~ "weekday"))

```

Make a panel plot containing a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).
```{r panelplot, echo=TRUE}
data3_group <- group_by(data3, interval, category2)
data3_sum1 <- summarise(data3_group, Number_of_steps = mean(steps))
#head(data3_sum1)

library(ggplot2)
ggplot(data3_sum1, aes(x = interval, y = Number_of_steps)) +
  geom_line() +
  facet_grid(rows = vars(category2))

dev.copy(png, file = "panelplot.png")
dev.off()

```


